A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-10-03 paper/paper.methods.tex
Clarify Branch-and-Cut relaxations

Currently, the most efficient approach to finding an exact solution for 
an ILP is called Branch-and-Cut~\cite{mitchell_branch-and-cut_2002}. 
This method involves iteratively solving 
LP relaxations versions of the ILP, then constraining the relaxed problems and
considering various sub-problems until it finds integral solutions to the 
original ILP.
The intermediate relaxations allow the variables to take on real values, 
and can be solved efficiently using the Simplex method~\cite{shamir_efficiency_1987}. The 
complexity of finding an optimal integral solution thus lies in the 
branching search structure of the approach.

>>>>

Currently, the most efficient approach to finding an exact solution for 
an ILP is called Branch-and-Cut~\cite{mitchell_branch-and-cut_2002}. 
This method involves iteratively solving 
LP relaxations of the ILP, then constraining the relaxed problems and
considering various sub-problems until it finds integral solutions to the 
original ILP.
In the intermediate relaxations, the integer assignment variables can
take on real values, allowing the problem to be solved efficiently using 
the Simplex method~\cite{shamir_efficiency_1987}. The 
complexity of finding an optimal integral solution thus lies in the 
branching search structure of Branch-and-Cut.
